### 2020-04-14 serial.tex
tweak

Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its basic reproduction number $\mathcal R_0$ \citep{majumder2020early}.
The basic reproduction number, which is defined as the average number of secondary cases caused by a primary case in a fully susceptible population, allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
Since the reproduction number cannot be measured directly, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions.

>>>>

Since the emergence of the novel coronavirus disease (COVID-19), a significant amount of research has focused on estimating its reproduction number $\mathcal R$ \citep{majumder2020early}.
The reproduction number is defined as the average number of secondary cases caused by a primary case;
the corresponding reproduction number in a fully susceptible population --- referred to as the basic reproduction number $\mathcal R_0$ --- allows us to predict the extent to which a disease will spread in the population and the amount of intervention to prevent an outbreak \citep{anderson1991infectious}.
Since the reproduction number cannot be measured directly, it is often estimated from the observed exponential growth rate using generation- and serial-interval distributions.
